% introduction.tex
%
% Author       : James Mnatzaganian
% Contact      : http://techtorials.me
% Date Created : 08/27/15
%
% Description  : Introduction chapter used by "thesis.tex".
%
% Copyright (c) 2015 James Mnatzaganian
%
% Version 2 ::
% Author       : Andres Kwasinski
% Contact      : https://people.rit.edu/axkeec/
% Date Created : 01/09/2020
%

% NOTE: All filler text has "TODO" written. This must be removed in the final copy!

\chapter{Introduction}\label{section:introduction}
\section{Motivation}
\todo{Mention something about lack of functional astrocyte model}
Biological neurons and neural networks originally inspired traditional,
real-valued ANNs. Decades of research and hardware advancements later, ANNs
have achieved and even surpassed humans in specialized tasks. Currently
neural networks outperform humans in object recognition and classification,
a variety of games (chess, go, some video games), and speech
recognition. This performance comes at a cost however, huge networks with
millions of parameters are needed. Computing their decision in real-time
requires specialized, power-hungry hardware, and their ability to handle
time-series data is limited. The human brain on the other hand, is able to
handle a wide variety of complex tasks with $\approx$ 20 W of power, and
seamlessly handle time-series input. Over the decades, research in the
neuroscience field has advanced as well and it is known that the sigmoid
neuron is poor approximation of a biological neuron. In addition
Neuroscientists have discovered a variety of temporal encoding schemes
beyond rate-based coding, suggesting that real values can't approximate
biological neuron communication. As the functional gap between biological
and artificial neurons is realized it is important to consider the
differences, and possible advantages to closing this gap. Spiking neural
networks, are a step in that direction and there is growing interesting in
exploring their properties. The goal of such research is generally to tease
out the elements of biological neural networks that facilitate low-power
processing of time-series data, in addition to low-power on-line
training. Achieving these things may require a fundamental shift in the
models used, a shift towards spiking neural networks. Reducing the power
requirement for a given task would be extremely beneficial from an
engineering perspective, but there are further implications. SNNs lend
themselves to more efficient, and simpler hardware implementations compared
to ANNs. Reducing the number of transistors required for a single neuron
could open doors for deeper and larger networks then would be feasible
today.
    
\section{Thesis Objectives}
%% The overarching goal of this thesis is to extend the bio-realism of spiking
%% networks by introducing an Astrocyte-like processing element. This Astrocyte
%% element will drive synaptic plasticity in a way that extends the commonly
%% used Spike Timing Defendant Plasticity rule, and offers improvements and
%% increased flexibility in the single and multi-synapses cases.

The overarching goal of this thesis is to develop a bio-inspired Astrocyte
model, and more broadly an Astrocyte-Neuron interaction model. This model will
be computationally simple, scalable, and captures common themes within
Neuroscience literature. To direct this research, the developed Astrocyte
element will drive synaptic plasticity; First generalizing, then diverging from
the widely used STDP rule. Benefits of Astrocyte-like control of synaptic
plasticity will be demonstrated in the single synapse, single neuron
configuration (1S1N) as well as select multi-synapse configurations. Inputs will
consist of procedurally generated spiking inputs. This would include poisson
rate-coded spike trains, spiking inputs representing Boolean variables, and
temporal inputs that follow specific patterns. To evaluate each experiment
different intrinsic properties will be observed, such as convergence/divergence
of weights, speed of convergence, stable points across a parameter space, and
lastly performance on any task driven experiments. Statistical analysis of
various intermediate signals, and weights may be employed as well.

More specific objectives.
\begin{enumerate}
  %% Specify -> developing a novel astrocyte model. Stress what is new and value-added
  \item To Develop an Astrocyte LIF-Neuron model based on bio-chemical pathways,
    capable of responding internally to pre and post-synaptic spikes. Explore
    these internal responses, and show stable configurations within the
    tripartite synapse.

  \item Show, in the case of a single spiking neuron with one input, how
    the developed Astrocyte-synapse model can drive synaptic plasticity in way
    that generalizes, and extends STDP.

  \item Extend the Developed Astrocyte-Synapse Model to include coordination of
    plasticity rules across multiple synapses, and show how this coordination is
    critical to a learning task.

\end{enumerate}
